\documentclass[letterpaper]{article}
\include{environment}
\usepackage[colorlinks=true, linkcolor=linkcolor]{hyperref}
\title{\projname{} - A Realtime Beat Tracker \\ Preliminary Synthesis Results}
\begin{document}

\maketitle

\section{Current Status}

    Timing issues that were discussed in the last meeting were resolved thanks
    to Asif's suggestions.  Bits are flowing end to end now and I'm working on
    making the algorithm correct.  I haven't had a chance to implement field
    narrowing yet, but I will attempt to do so within a week.  It should not
    represent a major area or timing constraint and so should not be a blocker
    that requires total redesign.

\section{Preliminary Synthesis Results}

    I've been designing this project very close to hardware -- I do live
    hardware testing just as much as I do simulation testing.  So I've been
    conscious of device timing and area constraints the entire time.

    I've been testing with just 3 metronomes. The synthesis results that the
    logic usage is absolutely tiny:

\begin{monospace}
Device utilization summary:
---------------------------

Selected Device : 3s700anfgg484-4 

 Number of Slices:           422  out of   5888     7%
 Number of Slice Flip Flops: 440  out of  11776     3%
 Number of 4 input LUTs:     769  out of  11776     6%
    Number used as logic:    729
    Number used as RAMs:      40
 Number of IOs:               36
 Number of bonded IOBs:       25  out of    372     6%
 Number of MULT18X18SIOs:      1  out of     20     5%
 Number of GCLKs:              2  out of     24     8%
 Number of DCMs:               1  out of      8    12%
\end{monospace}

Examining the timing analysis report, the critical path is through the beat
classifier, with the majority of the time is from the energy calculation path.

Let's take a look if we bump the number of metronomes up to 63:
\begin{monospace}
Device utilization summary:
---------------------------

Selected Device : 3s700anfgg484-4 

 Number of Slices:           2138  out of   5888    36%
 Number of Slice Flip Flops: 2806  out of  11776    23%
 Number of 4 input LUTs:     3934  out of  11776    33%
 Number of IOs:                36
 Number of bonded IOBs:        25  out of    372     6%
 Number of BRAMs:               1  out of     20     5%
 Number of MULT18X18SIOs:       1  out of     20     5%
 Number of GCLKs:               2  out of     24     8%
 Number of DCMs:                1  out of      8    12%
\end{monospace}

The critical path is once again through the beat classifier to the new beat
injector.

Right now, attempts at building with 120 metronomes fails to meet timing but I
bet I could probably get it to synthesize properly with some work.  This would
eliminate the need for field narrowing.


\end{document}
